hatchR: A toolset to predict hatch and emergence phenology in wild fishes

### 2025-03-07 inst/manuscript/paper.Rmd
Fix typo in Case Study 1

```{r, eval=FALSE, echo=FALSE}
# read in EFS data
EFS_data <- crooked_river

@@

# we care about when fish are out of gravel, so select emerge mod
bt_emerge_mod <- model_select(
  author = "Austin et al. 2017",
  species = "bull trout",
  model = "MM",
  development_type = "emerge"
)

@@

In this example, the model predicts that the last Bull Trout will emerge on April 21, before the June 1st road work target date. This suggests that the Fisheries Biologist can confidently approve the work in the area without concern for sediment disturbance impacting fish developing in the gravel. This type of predictive modeling helps managers make informed, science-based decisions that balance conservation priorities with land-use activities.

>>>>

```{r bt-emerge-crooked, eval=FALSE, echo=FALSE}
# read in EFS data
EFS_data <- crooked_river

@@

# we care about when fish are out of gravel, so select emerge mod
bt_emerge_mod <- model_select(
  author = "Austin et al. 2019",
  species = "bull trout",
  model = "MM",
  development_type = "emerge"
)

@@

In this example, the model predicts that the last Bull Trout will emerge on May 1, before the road work target date (June 1). This suggests that the Fisheries Biologist can confidently approve the work in the area without concern for sediment disturbance impacting fish developing in the gravel. This type of predictive modeling helps managers make informed, science-based decisions that balance conservation priorities with land-use activities.
